BOLD Parameter Estimation Using Particle Filters

### 2010-08-14 doc/thesis/thesis.tex
added a discussion and future work section. discussion and conclusion need more work.
updated title
fixes to results
more on the results. Updated the HRF and applied pierces recommendations

\usepackage{colortbl}
\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true]{hyperref}

@@

% TITLE
{\Large 
Full Volume Blood-Oxygen-Level-Dependent-Signal Parameter Estimation Using Particle Filters
}

@@

Master of Science \\
in \\
Electical Engineering

@@

Traditional methods of analyzing FMRI images use a linear combination of
just a few static regressors. This works demonstrates an alternative
approach using a physiologically inspired nonlinear model. By using a 
particle filter to optimize the model parameters, the computation time
is kept reasonable without requiring a linearization of the noise in the state
variables. The activation results show regions similar those found in 
SPM; however, there are some notable regions not detected by 
SPM. Though the parameters selected by the particle filter based approach
are more than sufficient to predict the BOLD response,
more model constraints are needed to uniquely identify a single set
of parameters. This ill-posed nature explains the large discrepancies
found in other research that attempted to characterize the model parameters.
For this reason the final distribution of parameters is more medically relevant
than a single estimate. Because the output of the particle filter is 
a full posterior probability, the reliance on the mean to estimate 
parameters is not strictly necessary. This work presents
not just a viable alternative to the traditional method of detecting
activation, but an extensible technique of estimating the joint BOLD
parameter distribution.

@@

\include{intro}
\include{background}
\include{particlefilters}
\include{methods}
\include{results}
\include{resultsB}
\include{conclusion}

\bibliographystyle{ieeetr}
%\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}

>>>>

 \usepackage[hang,small,bf]{caption}

\usepackage{colortbl}
\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true,linkcolor=black]{hyperref}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}

@@

% TITLE
{\Large 
Full Brain Blood-Oxygen-Level-Dependent Signal Parameter Estimation Using Particle Filters
}

@@

Master of Science \\
in \\
Electrical Engineering

@@

Traditional methods of analyzing FMRI images use a linear combination of
just a few static regressors. This works demonstrates an alternative
approach using a physiologically inspired nonlinear model. By using a 
particle filter to optimize the model parameters, the computation time
is kept below a minute per voxel without requiring a linearization 
of the noise in the state
variables. The activation results show regions similar those found in 
SPM; however, there are some notable regions not detected by 
SPM. Though the parameters selected by the particle filter based approach
are more than sufficient to predict the BOLD response,
more model constraints are needed to uniquely identify a single set
of parameters. This ill-posed nature explains the large discrepancies
found in other research that attempted to characterize the model parameters.
For this reason the final distribution of parameters is more medically relevant
than a single estimate. Because the output of the particle filter is 
a full posterior probability, the reliance on the mean to estimate 
parameters is not strictly necessary. This work presents
not just a viable alternative to the traditional method of detecting
activation, but an extensible technique of estimating the joint BOLD
parameter distribution.

@@

\include{intro}
\include{background}
\include{particlefilters}
\include{methods}
\include{results}
\include{resultsB}
\include{discussion}
\include{conclusion}

\bibliographystyle{plain}
%\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}
